Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-06 ms.tex
deleted comments to self that have already been addressed, added a couple of new comments to self
writing section about using Markov chains to evaluate goodness-of-fit of various dust SED models

Including 857 GHz, we thus have nine correlation slope constraints for six 
free parameters. Including DIRBE 140$\mu$m and 240$\mu$m is critical in making 
this problem sufficiently overconstrained, and also in providing information 
near the peak of the dust SED at $\sim$140$\mu$m, which is particularly 
sensitive to the presence of a single versus multiple MBB components. 
% last sentence mentioning
% that the large number of frequency channels and good coverage of the 
% dust SED peak were what made FIRAS so appropriate for FDS99 analysis ??

%All of the correlations are performed using 
%$1^{\circ}$ smoothed maps

% need to mention that this is all for the low HI mask !!!!
% should have a three panel figure illustrating linear fits of

@@

@@

\subsection{Global Parameters Revisited}
\label{sec:hier}
% discuss goodness of fit tests based on running Markov chains with different
% sets of global parameters

>>>>

Including 857 GHz, we thus have nine correlation slope constraints for six 
free parameters. Including DIRBE 140$\mu$m and 240$\mu$m is critical in making 
this problem sufficiently overconstrained, and also in providing information 
near the peak of the dust SED at $\sim$140$\mu$m, which is particularly 
sensitive to the presence of a single versus multiple MBB components.

@@

% also might be worth mentioning that the MCMC analysis involves constraints
% where the zero level matters, whereas the correlation slope analysis here
% renders the zero levels irrelevant

@@

\subsection{Global Parameters Revisited}
\label{sec:hier}

The posterior sampling framework thus far described also affords us an 
opportunity to cross-check the conclusions of the correlation slope analysis in
$\S$\ref{sec:global}. The basic idea will be to continue sampling the posterior
of Equation \ref{eqn:post}, but at low resolution ($N_{side}$=64), including 
all HFI bands as well as DIRBE 100$\mu$m, 140$\mu$m and 240$\mu$m, and 
switching to a uniform prior on $T_2$. Under these circumstances, the 
chi-squared corresponding to the best-fit parameters for each pixel, termed 
$\chi^2_p$, is simply $-2 \times log(P_{max})$. 
% maybe invent a term chi^2_p or something to 
% reduce potential confusion caused by notation

\begin{figure}
\begin{center}
\epsfig{file=chi2_dirbe.eps, width=3.3in}
\caption{\label{fig:chi2_dirbe} Testing }
\end{center}
\end{figure}

Because we seek to compare the goodness-of-fit for various dust SED models in 
the diffuse ISM, we restrict to a set of $\sim$10,800 pixels ($\sim$22\% of the
sky), with $|b|>30^{\circ}$ and $|\beta|>10^{\circ}$. We also avoid the SMICA 
inpainting mask, pixels with appreciable CO contamination, and compact sources.
The goodness-of-fit `objective function' we employ to judge the quality of 
a particular dust SED model is $\langle \chi^2_p \rangle$, where the average 
is taken over the aforementioned set of $\sim$10,800 pixels. 
$\langle \chi_{p}^2 \rangle$ is also equivalent to the reduced chi-squared, 
$\chi^2_{\nu}$, when considering the total number of free parameters to be the 
number of pixels multiplied by the number of free parameters per pixel, and 
similarly for the total number of constraints.

We calculate $\chi^2_{\nu}$ for various dust SED models, independently 
minimizing each $\chi^2_p$ by finding pixel $p$'s best-fitting dust 
temperature and normalization, then evaluating $\langle \chi_{p}^2 \rangle$. 
First, we considered single-MBB models with $\beta$ spatially constant (see the
black line in Figure \ref{fig:chi2_dirbe}). $\beta$=1.57 yields the best fit, with 
$\chi^2_{\nu}$=2.51. This result is in excellent agreement with that of 
$\S$\ref{sec:global}, where we found the best-fit single-MBB model to have 
$\beta$=1.59.

% mention other single MBB variants

Next, we calculate $\chi^2_{\nu}$ for the two-component model with global 
parameters from FDS99 (Table \ref{tab:global}, model 2). We find 
$\chi^2_{\nu}$=2.33, a slight improvement relative to the $\beta$=1.59 
single-MBB model. Finally, calculate $\chi^2_{\nu}$ for Table \ref{tab:global} 
model 3, the two-component model favored by our \PLANCK+DIRBE correlation 
slopes. In this case, we achieve the best goodness-of-fit out of the all the 
models tested, with $\chi^2_{\nu}$=2.11.

% could compare temperatures, but masks are different

% discuss goodness of fit tests based on running Markov chains with different
% sets of global parameters

% also should emphasize that an important difference here relative to the
% correlation slope analysis is that here, the zero levels actually do matter
